### 2019-01-17 manuscript/manuscript.rmd
added model results

```{r preliminaries}
library( tidyverse )
library( magrittr )
library( viridis )

@@

@@

plot_matrix = function( R_matrix ){
	D = data.frame( R_matrix )
	D$source = row.names(D)
	Dg = gather( D, 1:20, key=dest, value=exch, -source )
	Dg %<>%
		mutate( source=factor(source, levels=aa_functional)  ) %>%
		mutate( dest=factor(dest, levels=aa_functional)  )

	Dg %>%
		ggplot(aes(x=dest, y=source)) + 
		geom_tile(aes(fill=exch)) +
		scale_fill_gradient2()
}

@@

plot_matrix(wag_matrix)
plot_matrix(lg_matrix)

@@

plot_matrix(lg_wag_diff)

@@

plot_matrix( lg_wag_diff_thresh )

>>>>

```{r preliminaries}
library( tidyverse )
library( magrittr )
library( viridis )
library( knitr )
library( gridExtra )

@@

```{r modelfinder}

analyses_new %>% 
	filter(modelfinder==TRUE) %>% 
	select( matrix, clade, result, model_summary ) %>%
	kable()

Table XXModelfinder. The models selected by modelfinder for each matrix.

@@

plot_matrix = function( R_matrix, title=NULL ){
	D = data.frame( R_matrix )
	D$source = row.names(D)
	Dg = gather( D, 1:20, key=dest, value=exch, -source )
	Dg %<>%
		mutate( source=factor(source, levels=aa_functional)  ) %>%
		mutate( dest=factor(dest, levels=aa_functional)  )

	Dg %>%
		ggplot(aes(x=dest, y=source)) + 
		geom_tile(aes(fill=exch)) +
		scale_fill_gradient2() +
		ggtitle(title)
}

@@

@@

@@

grid.arrange(
	plot_matrix(lg_matrix, title="(A) LG matrix"),
	plot_matrix(wag_matrix, title="(B) WAG matrix"),
	plot_matrix(lg_wag_diff, title="(C) LG - WAG"),
	plot_matrix( lg_wag_diff_thresh, title="(D) Thresholded LG - WAG" )
)
